Kontrola CES × MUSEION

### 2023-06-02 _GEN_CES.Rmd
OMCV CES in progress

petky <- c("B", "CV-N", "CV-S", "G", "K-N", "K-S", "Li", "M", "pB", "pCV-N", "pG", 
           "pK-N", "pLi", "pM", "pMO", "pT", "T") 
ctyrky <- c("B-sken", "C", "Ck", "Dt", "Eg", "Et", "F", "Fa", "H", "IT", "La", "Le", 
            "Li-sken", "Mi","M-sken", "MT", "MTč", "N", "NDa", "NDo", "NDp", "NDvz", 
            "Ng", "Ng-f", "Nu", "O", "Ok", "P", "Pc", "Pc-K", "Pl", "Plk", "pom", 
            "PS", "PS-kn", "PS-ko", "PS-kr", "PS-pr", "PS-v", "R", "S", "S-K", "ST", 
            "TR", "T-sken", "Tx", "ZM")

@@

# ces_ic <- ic %>% 
#   mutate(Mrada = str_replace_all(cislo, "[:digit:]+", ""),
#          Mrada = str_trim(Mrada),
#          Mcislo = str_extract(cislo, "[:digit:]+"),
#          Mcislo_0 = case_when(Mrada %in% trojky ~ str_pad(Mcislo, 3, pad = "0"),
#                               Mrada %in% ctyrky ~ str_pad(Mcislo, 4, pad = "0"),
#                               Mrada %in% petky ~ str_pad(Mcislo, 5, pad = "0"),
#                               TRUE ~ Mcislo), 
#          Mrada0 = case_when(Mrada == "CV - N" ~ "CV-N",
#                            Mrada == "L" ~ "chybi",
#                            Mrada == "La x" ~ "La",
#                            Mrada == "LE" ~ "Le",
#                            Mrada %in% c("M T č /", "MT č", "MT č /", "MT č /-", "MT č //",
#                                         "MT č //-", "MT č //,", "MT č //,-", "MT č //a",
#                                         "MT č /a", "MTč/") ~ "MTč",
#                            TRUE ~ Mrada)) %>% 
#   unite(MINVC, c(Mrada, Mcislo_0), sep = "", na.rm = T, remove = F)

ces_ic <- ic %>%
  mutate(Mrada = case_when(
    str_detect(cislo, "^[:alpha:]{2}\\s\\d+") ~ str_extract(cislo, "^[:alpha:]{2}"), # Ng 5
    str_detect(cislo, "^[:alpha:]{2}\\s[:alpha:]+\\s\\d+") ~ str_extract(cislo, "^[:alpha:]{2}\\s[:alpha:]+"), # "Pl CV" "Pl K" 
    str_detect(cislo, "\\w+-\\w+\\s.*") ~ str_extract(cislo, "\\w+-\\w+"), # "K-S", "CV-N"
    str_detect(cislo, "^[:upper:]\\s.*") ~ str_extract(cislo, "^[:upper:]"), # B 10
    str_detect(cislo, "^[:upper:]{2}\\s\\w\\s\\d+") ~ str_extract(cislo, "^[:upper:]{2}\\s\\w"), # ND o 110
    str_detect(cislo, "CV - N") ~ "CV-N",
    str_detect(cislo, "^Li.*") ~ "Li",
    str_detect(cislo, "^PcK.*") ~ "Pc K",
    str_detect(cislo, "^s Cv\\s\\d+") ~ "S CV",
    str_detect(cislo, "^s\\s\\d+") ~ "S",
    str_detect(cislo, "^Et\\d+") ~ "Et",
    str_detect(cislo, "^[:upper:]\\d+") ~ str_extract(cislo,"^[:upper:]"), # O2703
    str_detect(cislo, "^MTč\\d+") ~ "MTč",
                           TRUE ~ "chybny format invc"))

# C CV 143	1	Jiná_-_Cín.txt	C

sample_n(ces_ic, 10)

@@

@@

rel0 <- full_join(ces_ic, mus_ic, by = c("MINVC" = "sp_cislo"), keep = T) 
  select(-sp_porcislo, -sp_porcislosub, -sp_porcislodo, -sp_porcislosub_1, -kod) %>% 
  rename(CEScislo = cislo.x, cislo_podsb = cislo.y)

rnd <- sample_n(rel0, 10)
```

>>>>

petky <- c("B", "CV-N", "CV-S", "G", "K-N", "K-S", "Li", "M", "pB", "pCV-N", "pG", 
           "pK-N", "pLi", "pM", "pMO", "pT", "T") 
ctyrky <- c("B-sken", "C", "CK", "Dt", "Eg", "Et", "F", "Fa", "H", "IT", "La", "Le", 
            "Li-sken", "Mi","M-sken", "MT", "MTč", "N", "NDa", "NDo", "NDp", "NDvz", 
            "Ng", "Ng-f", "Nu", "O", "Ok", "P", "Pc", "Pc-K", "Pl", "Plk", "pom", 
            "PS", "PS-kn", "PS-ko", "PS-kr", "PS-pr", "PS-v", "R", "S", "S-K", "ST", 
            "TR", "T-sken", "Tx", "ZM")

@@

# CCV, L -> nejsou vubec

ces_ic <- ic %>%
  mutate(Mrada_patt = case_when(
    str_detect(cislo, "^[:alpha:]{2}\\s\\d+") ~ str_extract(cislo, "^[:alpha:]{2}"), # Ng 5
    str_detect(cislo, "^[:alpha:]{2}\\s[:alpha:]+\\s\\d+") ~ str_extract(cislo, "^[:alpha:]{2}\\s[:alpha:]+"), # "Pl CV" "Pl K" 
    str_detect(cislo, "\\w+-\\w+\\s.*") ~ str_extract(cislo, "\\w+-\\w+"), # "K-S", "CV-N"
    str_detect(cislo, "^[:upper:]\\s\\d+") ~ str_extract(cislo, "^[:upper:]"), # B 10
    str_detect(cislo, "^[:upper:]\\s[:upper:]+.*") ~ str_extract(cislo, "^[:upper:]\\s[:upper:]+"), # C CV
    str_detect(cislo, "^[:upper:]{2}\\s\\w\\s\\d+") ~ str_extract(cislo, "^[:upper:]{2}\\s\\w"), # ND o 110
    str_detect(cislo, "^[:upper:]\\d+") ~ str_extract(cislo,"^[:upper:]"), # O2703
    TRUE ~ "chybny format invc"),
    Mrada_edit = case_when(str_detect(cislo, "^Li.*") ~ "Li",
                           str_detect(cislo, "^PcK.*") ~ "Pc-K",
                           str_detect(cislo, "^Pc K.*") ~ "Pc-K",
                           str_detect(cislo, "^s Cv\\s\\d+") ~ "S CV",
                           str_detect(cislo, "^s\\s\\d+") ~ "S",
                           str_detect(cislo, "^Et\\d+") ~ "Et",
                           str_detect(cislo, "^MTč\\d+") ~ "MTč",
                           str_detect(cislo, "CV - N") ~ "CV-N",
                           str_detect(Mrada_patt, "PS") ~ str_replace(Mrada_patt, "PS", "Ps"),
                           str_detect(Mrada_patt, "CK") ~ "Ck",
                           str_detect(Mrada_patt, "LE") ~ "Le",
                           str_detect(Mrada_patt, "Mt") ~ "MT",
                           str_detect(Mrada_patt, "Pl K") ~ "Plk",
                           str_detect(Mrada_patt, "Rš") ~ "Rs",
                           str_detect(Mrada_patt, "sK") ~ "S-K",
                           TRUE ~ Mrada_patt),
    Mrada = gsub(" ", "", Mrada_edit),
    Mcislo = case_when(
      str_detect(cislo, "\\d+\\/.+") ~ str_extract(cislo, "\\d+\\/.+"), # Ng 5)
      str_detect(cislo, "\\d+") ~ str_extract(cislo, "\\d+"), # Ng 5)
      TRUE ~ "chybny format invc"),
    Mcislo_0 = case_when(Mrada %in% trojky ~ str_pad(Mcislo, 3, pad = "0"),
                         Mrada %in% ctyrky ~ str_pad(Mcislo, 4, pad = "0"),
                         Mrada %in% petky ~ str_pad(Mcislo, 5, pad = "0"),
                         TRUE ~ Mcislo),
    Msubc = ifelse(str_detect(Mcislo_0, "\\/.+"), gsub(".+\\/", "", Mcislo_0), NA),
    Mcislo_0 = ifelse(str_detect(Mcislo_0, "\\/.+"), gsub("\\/.+", "", Mcislo_0), Mcislo_0),
    MINVC = ifelse(is.na(Msubc), paste0(Mrada, Mcislo_0), paste0(Mrada, Mcislo_0, "/", Msubc)))

check <- ces_ic %>% select(Mrada_patt, Mrada_edit, Mrada) %>% distinct()

print(sample_n(ces_ic, 10))

@@

```{r, warning = F}

@@

rel0 <- full_join(ces_ic, mus_ic, by = c("MINVC" = "sp_cislo"), keep = T) %>% 
  select(-sp_porcislo, -sp_porcislosub, -sp_porcislodo,-sp_porcislosubdo)

sample_n(rel0, 10)
```
